Competing Bandits: The Perils of Exploration under Competition

### 2018-09-01 paper/content/inverted_u.tex
editing...

In this section we document the results of the competition game for various parameterizations of our model. We consider three separate settings for our model: permanent monopoly, temporary monopoly (incumbent vs entrant), and permanent duopoly.

@@

We interpret the move from permanent monopoly to temporary monopoly and temporary monopoly to permanent duopoly as increases in competition. We believe this is reasonable and consistent with the empirical results which define increases in competition as increases in a measure of market power (1 - the Lerner Index). In our model we have no prices and no costs and so we interpret increases in ``market power" as decreases in the number of rounds where a firm has to compete for agents.

% couldn't get section references to work so hardcoding for now
We utilize the same instances and realizations as in the section 3  and simulate the model described in section 2. We initially take the strategies of the firms as exogenous (chosen from $\mathcal{A}$) and simulate the model given these strategies in order to determine the expected payoffs associated with each pair of algorithms. Unless otherwise noted, all the results are reported at $t = 2000$.

\textbf{Permanent Monopoly} Under permanent monopoly only a single firm exists in the market for every period. In our model the firm only gets utility from a larger market share so it is indifferent between each algorithm in $\mathcal{A}$ since, regardless of the algorithm it deploys, it will get the entire market. If we suppose that deploying the ``better" algorithms has even an $\epsilon > 0$ cost or, equivalently, that firms break indifference towards algorithms that are easier to deploy, then the firm would choose to deploy $\DG$.

\textbf{Permanent Duopoly} Permanent duopoly corresponds to the model described in section 2 where $X = 0$ so that both firms enter the market simultaneously. What algorithms are firms incentivized to deploy? We report the average market share taken over the $N$ simulations for a set of exogenous values of $T_0$. Additionally, we report the mean and median of an additional quantity which we define as the \textit{effective end of game}.

@@

\end{document}

>>>>

\swedit{Now we demonstrate the inverted-U relationship between the
  incentivized algorithms and the competition levels in the game. In
  the order of increasing competition levels, we study three different
  settings: permanent monopoly, temporary monopoly, and permanent
  duopoly. In more details:}

@@

\swdelete{We interpret the move from permanent monopoly to temporary monopoly and temporary monopoly to permanent duopoly as increases in competition. We believe this is reasonable and consistent with the empirical results which define increases in competition as increases in a measure of market power (1 - the Lerner Index). In our model we have no prices and no costs and so we interpret increases in ``market power" as decreases in the number of rounds where a firm has to compete for agents.

% couldn't get section references to work so hardcoding for now
We utilize the same instances and realizations as in the section 3  and simulate the model described in section 2. We initially take the strategies of the firms as exogenous (chosen from $\mathcal{A}$) and simulate the model given these strategies in order to determine the expected payoffs associated with each pair of algorithms. Unless otherwise noted, all the results are reported at $t = 2000$.
}

\swedit{\xhdr{Permanent Monopoly.} There is only a single firm in the market
for the entire period. In this case, the firm will can the entire
market, regardless what algorithm it deploys. Assuming the deployment
of any exploration algorithms will incur certain cost, then the firm
would choose to deploy $\DG$.}

\xhdr{Permanent Duopoly} Permanent duopoly corresponds to the model described in section 2 where $X = 0$ so that both firms enter the market simultaneously. What algorithms are firms incentivized to deploy? We report the average market share taken over the $N$ simulations for a set of exogenous values of $T_0$. Additionally, we report the mean and median of an additional quantity which we define as the \textit{effective end of game}.

@@

\end{document}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../competing_bandits"
%%% End:
